Multiset-Trie Data Structure

### 2023-03-15 tex/algorithms-2122309-proof.tex
a paragraph added to related work (omitted in the previous version).

The index structures for the efficient implementation of the (multi)set containment queries were studied in the framework of the relational DBMS as well as the object-relational DBMS, where we can use multivalued attributes, including sets, multisets (bags), and lists. Zhang et al.\ \cite{Zhang2001} compared the performance of the containment queries implemented in a standard relational DBMS (RDBMS) to an information retrieval engine. The results show that, in general, the IR engine performs better than an RDBMS on containment queries. They identified the problems that lead to the poor performance of the containment operations in an RDBMS and showed that, with some modifications, an RDBMS could perform this class of queries more efficiently.

>>>>

The index structures for the efficient implementation of the (multi)set containment queries were studied in the framework of the relational DBMS as well as the object-relational DBMS, where we can use multivalued attributes, including sets, multisets (bags), and lists. Zhang et al.\ \cite{Zhang2001} compared the performance of the containment queries implemented in a standard relational DBMS (RDBMS) to an information retrieval engine. The results show that, in general, the IR engine performs better than an RDBMS on containment queries. The significant causes that differentiate the performance of the IR and RDBMS implementations are the join algorithms employed and the hardware cache utilization. The differences in join algorithms and the cache access method that makes IR queries faster were identified precisely. First, the multi-predicate merge join of the IR engine is different from the standard merge join, and the index nested-loop join algorithms. Second, the study of the utilization of cache in the multi-predicate merge join, standard merge join, and index-nested loop joins has been done, identifying more precisely the differences in the algorithms. They have presented that with some modifications, an RDBMS could perform this class of queries more efficiently.
